Gamification Effectiveness on Education

### 2024-04-15 paper/paper.qmd
added a paragraph on the data cleaning prodecure

# Data {#sec-data}

@@

@@

## First discussion point {#sec-first-point}

@@

# Model details {#sec-model-details}

>>>>

# Data

## 2.1 Background of Original Study

@@

## 2.2 Data Cleaning Procedure

For our replication, we drop 20 rows of data from the original dataset provided since those rows contained missing data on grades of some assessments and final examination. The age row was removed since in the original study it mention that there age range for each group but in the dataset provided they made every value in that column to 19 since that the average age in the study.

@@

## First discussion point

@@

# Model details
